Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-04-23 paper.tex
Discuss the experimental setup in more detail

Experiments were performed in the University of New Hampshire's tow/wave tank
turbine test bed. The turbine model is dubbed the UNH-RVAT, for Reference
Vertical Axis Turbine, which is designed to be a generic case for numerical
model testing, similar to the Sandia National Labs/US Department of Energy RM2
River Turbine, but with higher solidity, or blade chord to radius ratio. Details
of the turbine and experimental setup, shown in Figure~\ref{fig:turbine} and
Figure~\ref{fig:exp-setup}, respectively, are described in
\cite{Bachant2015-JoT}, and a CAD model of the turbine is available from
\cite{Bachant2014-RVAT-CAD}.

@@

@@

>>>>

Experiments were performed in the University of New Hampshire's tow/wave tank
turbine test bed. The turbine model is dubbed the UNH-RVAT, for Reference
Vertical Axis Turbine, which is designed to be a generic case for numerical
model testing, similar to the Sandia National Labs/US Department of Energy RM2
River Turbine, but with higher solidity, or blade chord to radius ratio. A CAD
model of the turbine, depicted in \ref{fig:turbine}, is available from
\cite{Bachant2014-RVAT-CAD}.

@@

The turbine was mounted in a frame constructed from NACA 0020 sections. The
turbine shaft ran up through the water surface, coupled to a permanent magnet
servo motor with a 20:1 gearbox. This servo was controlled by the tow tank's
main motion controller for high synchronization with the carriage motion. A
rotary torque transducer was installed inline between the servo and the turbine,
and the servo was also mounted on a slewing ring bearing, which allowed a
redundant measurement of torque via an arm and load cell used to counteract the
turbine moment. The frame was mounted to the carriage via linear guides, such
that the total streamwise drag force was transferred to a pair of S-beam load
cells, providing the rotor drag measurements, after a measured tare drag was
subtracted in post processing. Similarly, a tare torque was measured by rotating
the turbine shaft in air. Turbine angular and tow carriage linear position were
measured using quadrature encoder signals, with $10^5$ counts-per-rev for the
turbine and 10 $\mathrm{\mu m}$ resolution for the carriage position. These
signals, along with the torque and drag signals, were sampled at 2 kHz.

@@

Wake velocity was measured using a Nortek Vectrino+ acoustic Doppler velocimeter
(ADV), sampling at 200 Hz. The probe was mounted on an automated positioning
system, also controlled by the tow tank's main motion controller. The ADV and
DAQ systems' sampling times were synchronized by triggering the start of data
acquisition via a pulse sent from the motion controller.
